Xolotl: An Intuitive and Approachable Neuron \& Network Simulator in MATLAB

### 2018-07-10 paper/paper.tex
made fonts on first two figs bigger

\begin{figure}
	\centering
	\includegraphics[width=1.0\linewidth]{gfx/figure_HH}
	\caption{\texttt{xolotl} makes it easy tp set up and simulate conductance-based models. Schematic representation of a single-compartment neuron with three populations of ion channels (colored rectangles). In the simulator, the soma is represented using an object of class $compartment$ and the populations of ion channels are represented by $conductance$ objects contained within the compartment object. The code snippet shown sets up this neuron model, injects current, integrates and plots the voltage, and shows activation functions, all in a few lines of code. (A) Simulated voltage trace of a Hodgkin-Huxley model with three conductances and 0.2 nA of injected current. Colors indicate the dominant current (gold is fast sodium (NaV), blue is delayed rectifier (Kd), red is Leak). (C) f-I curve of this neuron. (D-E) Steady-state gating functions for activation (m) and inactivation (h) gating variables. (F-I) Voltage-dependence of time constants for activation (m) and inactivation (h) gating variables}
	\label{fig:figurehh}
\end{figure}

\begin{figure}[!htb]
	\centering
	\includegraphics[width=1.0\linewidth]{gfx/figure_clamp}
	\caption{Simulating a voltage-clamp experiment. The diagram shows a cell with delayed rectifier potassium conductance (\cite{liuModelNeuronActivitydependent1998}) that is being recorded from in two-electrode voltage clamp. The code snippet shown here sets up a model with a single compartment and a single channel type, and clamps the cell to a constant voltage and integrates it. (A) Voltage steps that the cell is clamped to. (B) Current injected into the cell required to clamp it to the voltages in (A). (C) Asymptotic clamped current $vs.$ clamped voltage for this cell. (D) Accounting for the reversal potential of Potassium ions yields the conductance-voltage curve of this channel type. (E) Normalized conductance-voltage curves, with sigmoid fits with various exponents. (F) An exponent of $n=4$ yields the best fit, allowing for the characterization of the activation function of this channel type. }
	\label{fig:figureclamp}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=1.0\linewidth]{gfx/figure_HH}
	\caption{Setting up a single-compartment model and injecting current into it. (A) Schematic representation of a single-compartment neuron with three populations of ion channels (colored rectangles). (B) In the simulator, the soma is represented using an object of class $compartment$ and the populations of ion channels are represented by $conductance$ objects contained within the compartment object. (C) The code snippet shown sets up this neuron model, injects current, integrates and plots the voltage, and displays activation functions, all in a few lines of code. (D) Simulated voltage trace of a Hodgkin-Huxley model with three conductances and 0.2 nA of injected current. Colors indicate the dominant current (gold is fast sodium (NaV), blue is delayed rectifier (Kd), red is Leak). (E) firing rate $vs$. current (f-I) curve of this neuron. (F-G) Steady-state gating functions for activation (m) and inactivation (h) gating variables. (H-I) Voltage-dependence of time constants for activation (m) and inactivation (h) gating variables}
	\label{fig:figurehh}
\end{figure}

\begin{figure}[!htb]
	\centering
	\includegraphics[width=1.0\linewidth]{gfx/figure_clamp}
	\caption{Simulating a voltage-clamp experiment. (A) The diagram shows a cell with delayed rectifier potassium conductance (from \cite{liuModelNeuronActivitydependent1998}) that is being recorded from in two-electrode voltage clamp. (B) The code snippet shown here sets up a model with a single compartment and a single channel type, and clamps the cell to a constant voltage and integrates it. (C) Voltage steps that the cell is clamped to. (D) Current injected into the cell required to clamp it to the voltages in (C). (E) Asymptotic clamped current $vs.$ clamped voltage for this cell. (F) Accounting for the reversal potential of Potassium ions yields the conductance-voltage curve of this channel type. (G) Normalized conductance-voltage curves, with sigmoid fits with various exponents. (H) An exponent of $n=4$ yields the best fit, allowing for the characterization of the activation function of this channel type. }
	\label{fig:figureclamp}
\end{figure}
